
---
title: "An Introduction to the Tidyverse"
author: "Brittany Barker"
date: 3/16/23
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(here) # Start in R project directory
library(dplyr) # Data wrangling
library(tidyr) # Data re-structuring
library(ggplot2) # Plotting model outputs
library(ggh4x) # For strip text in plots
library(ggsignif) # Showing significant differences between groups in plots
library(knitr) # Including graphics
library(agridat) # Agricultural data
```

## About me

:::: {.columns}

::: {.column width="40%"}

:::

::: {.column width="60%"}
**Current position**  
- Research Associate, Oregon IPM Center, OSU  
<br/>
**Research interests**  
- Modeling, ecology, biogeography, conservation, biological invasions, and genetics  
<br/>
**Hobbies**  
- Running, hiking, biking, moving!  
- Gardening, native habitat restoration  
<br/>
**PDX R User Group**  
- Helped organize Aggregate since ~2021  
<br/>
  
:::

::::

## Cascadia R Conference 2023

Abstract submission is open until 3/30/23

```{r, echo = FALSE}
```

## This is one of my first presentations in `revealjs`!

